% -*- LaTeX -*-

% PLEASE USE THIS FILE AS A TEMPLATE FOR THE DOCUMENTATION OF YOUR OWN
% FACILITIES: IN PARTICULAR, IT IS IMPORTANT TO NOTE COMMENTS MADE IN
% THE TEXT AND TO FOLLOW THIS ORDERING. THE FORMAT FOLLOWS ONE USED BY
% THE COBE-DMR PROJECT.	
% A.J. Banday, April 1999.

\documentclass[12pt,twoside]{article}
\usepackage{healpix,html,graphicx,makeidx}
\begin{htmlonly}
\renewcommand{\ell}{l}
%\renewcommand{\lq}{`}
\renewcommand{\lq}{'}
\input{hpxversion}
\end{htmlonly}
\newcommand{\nside}{{N_{\rm side}}}
%% \renewcommand{\contentsname}{{TABLE OF CONTENTS\\
%% \rule{\hsize}{0.7mm}\\}}
%\newcommand{\myhtmlimage}[1]{\htmlimage{#1}}
\newcommand{\myhtmlimage}[1]{ }
\renewcommand{\contentsname}{{TABLE OF CONTENTS}}

\newcommand{\linklatexhtml}[3]{% \linklatexhtml{name}{latex_target}{html_target}
\latexhtml{\htmladdnormallink{#1}{#2}}{\htmladdnormallink{#1}{#3}}}

\sloppy
\setcounter{secnumdepth}{0}
\setcounter{tocdepth}{10}

\begin{document}
\title{\healpix Fortran Facility User Guidelines}
\docrv{Version \hpxversion}
\author{Eric Hivon, Frode K.~Hansen, Benjamin D.~Wandelt, Krzysztof M.~G\'orski,
Anthony J.~Banday, Martin Reinecke}
\abstract{This document describes the \healpix Fortran stand-alone facilities}
\date{\today}

\frontpage
%\newpage
\tableofcontents
\newpage

\section{Using the \healpix Fortran 90 facilities}
\label{section:defdir}
{\bf {Default File Names and Directories}}: for some applications, the \healpix facilities
require some precalculated input files describing the pixel window
function and quadrature ring weight (shipped as {\tt
Healpix/data/pixel\_window\_n????.fits} and {\tt
Healpix/data/weight\_ring\_n?????.fits} respectively). \label{page:defdir}

By default, files with the very same name will be looked for into: the current directory (.), the parent directory (..),
./data, ../data, \$HEALPIX and \$HEALPIX/data where \$HEALPIX is
a system variable defined as the full path to the \healpix package
(see the installation documentation).
The user has the possibility to change both the name of those files
and their location.

%% \vskip 1cm
%% {\bf {Input and Output Precision}}: several facilities offer the option of
%% changing the input and output data arrays from single to double precision
%% floating point reals. The following points should be noted: \label{page:ioprec}
%% \begin{itemize}
%% \item Double precision IO facilities can read indifferently single and double
%%   precision data files (and the same is true for single precision facilities). On
%%   the other hand, a double (resp. single) precision facility will only output double
%%   (single) precision  files.
%% \item Since the internal calculations sensitive to numerical round-off error
%%   (like the spherical harmonics recurrence) are
%%   {\em always} performed in double precision, switching to double precision IO
%% \begin{itemize}
%% \item   will have a limited impact on the output accuracy if the input file contains
%%   single precision data,
%% \item is recommended if the input file contains double precision data,
%% \item will not alter the execution speed, but
%%   it will almost double the memory consumption.
%% \end{itemize}
%% \end{itemize}
\vskip 1cm
{\bf {Double/Single Precision mode}}: several facilities offer the option of switching at run time 
the precision of the internal variables and arrays and of the I/O data from single to double precision
floating point reals. The following points should be noted: \label{page:ioprec}
\begin{itemize}
\item Facilities running in double precision mode can read indifferently single and double
  precision data files (and the same is true for single precision facilities). On
  the other hand, a double (resp. single) precision facility will only output double
  (single) precision  files.
\item Since the internal calculations sensitive to numerical round-off error
  (like the spherical harmonics recurrence) are
  {\em always} performed in double precision, switching to double precision mode
\begin{itemize}
\item   will have a limited impact on the output accuracy if the input file contains only
  single precision data,
\item is recommended if the input file contains double precision data, and the precision of the output is critical
\item will not alter the execution speed, but
  it will almost double the memory consumption of the facility,
\item will obviously double the size of the output file(s).
\end{itemize}
\end{itemize}

\newpage

\section[Changes between releases 2.20 and ??]{Changes between releases 2.20 and
??}
\begin{itemize}
	\item introduction of \htmlref{{\tt process\_mask}}{fac:process_mask} to
apodize a binary mask
	\item \htmlref{{\tt sky\_ng\_sim}}{fac:sky_ng_sim} now allows the computation
of the spatial derivatives of the non Gaussian map being produced, and the
output of the $a_{lm}$ coefficients of that map.
\end{itemize}


\section[Changes between releases 2.14 and 2.20]{Changes between releases 2.14 and
2.20}
\begin{itemize}
	\item faster 
\htmlref{{\tt synfast}}{fac:synfast},
\htmlref{{\tt anafast}}{fac:anafast},
\htmlref{{\tt smoothing}}{fac:smoothing} thanks to {\tt libpsht} routines. 
	\item most facilities can handle maps with $\nside > 8192$, ie more than
805,306,368 pixels.
\end{itemize}
See
\linklatexhtml{``F90 Subroutines Overview''}{subroutines.pdf}{subroutines.htm}
for details.

{\footnotesize{%
%%%%%%%%%%%%%%%%%%%
\section[Older Changes]{Older Changes}
\subsection[Changes between releases 2.13 and 2.14]{Changes between releases 2.13 and
2.14}
\begin{itemize}
\item In \htmlref{{\tt synfast}}{fac:synfast} facility, a numerical bug affecting the accuracy of the Stokes parameter derivatives 
$\partial X/\partial\theta$, 
$\partial^2 X/(\partial\theta\partial\phi\sin\theta)$, 
$\partial^2 X/\partial \theta^2$, 
for $X=Q,U$ has been corrected. See \htmlref{this appendix}{sec:bug_synder} for details.
\end{itemize}

\subsection[Changes between releases 2.0 and 2.1]{Changes between releases 2.0 and
2.1}
\begin{itemize}
\item The \htmlref{{\tt anafast}}{fac:anafast} facility can now compute the cross-correlations of two different
maps. 
\item The \htmlref{{\tt sky\_ng\_sim}}{fac:sky_ng_sim} facility (Rocha et al, 2005), to produce non-Gaussian CMB temperature maps,
has been added.
\end{itemize}

\subsection[Changes between releases 1.2 and 2.0]{Changes between releases 1.2 and 2.0}
\begin{itemize}
\item faster implementation of $a_{lm}$ related facilities, generalization of
  OpenMP parallelization, and availability of MPI parallelized routines (see
  mpi\_* routines in {\bf Fortran90 Subroutines Overview} document).
\item introduction of \htmlref{{\tt alteralm}}{fac:alteralm} facility to modify and/or rotate the spherical
  harmonics coefficients $a_{lm}$ and greater flexibility for constraining
  $a_{lm}$ in {\tt synfast}
\item single and double precision implementation of most facilities (see {\bf {Input and Output Precision}}
  page~\pageref{page:ioprec})
\end{itemize}
}}%%%%%%%%%%%%%%%%%%

\newpage

\include{alteralm}
\include{anafast}
\include{hotspot}
\include{map2gif}
\include{median_filter}
\include{plmgen}
\include{process_mask}
\include{smoothing}
\include{sky_ng_sim}
\include{synfast}
\include{ud_grade}

% \hspace{5cm}
% \begin{minipage}{5cm}
% \begin{itemize}
% \item \textbf{ANAFAST}
% \item \textbf{HOTSPOT}
% \item \textbf{MAP2GIF}
% \item \textbf{PLMGEN}
% \item \textbf{SMOOTHING}
% \item \textbf{SYNFAST}
% \item \textbf{UD\_GRADE}

% \end{itemize}
% \end{minipage}

% \clearpage

% \input{anafast}
% \input{hotspots}
% \input{map2gif}
% \input{plmgen}
% \input{smoothing}
% \input{synfast}
% \input{ud_grade}

\newpage
\include{fac_appendix}

\end{document}
