
\sloppy


\title{\healpix Fortran Subroutines Overview}
\docid{fits2cl*} \section[fits2cl*]{ }
\label{sub:fits2cl}
\docrv{Version 2.0}
\author{Eric Hivon, Frode K.~Hansen}
\abstract{This document describes the \healpix Fortran90 subroutine FITS2CL.}

\begin{facility}
{This routine reads a power spectrum or beam window function from a FITS ASCII
or binary table. 
The routine can read temperature coefficients $C_\ell^{TT}$ or both temperature and 
polarisation coefficients $C_\ell^{TT}$, $C_\ell^{EE}$, $C_\ell^{BB}$, $C_\ell^{TE}$ (and  
$C_\ell^{TB}$, 
$C_\ell^{EB}$, 
$C_\ell^{ET}$, 
$C_\ell^{BT}$, 
$C_\ell^{BE}$ when applicable). If the 
keyword PDMTYPE is found in the header, fits2cl assumes the table to be in the 
special format used by {\em Planck} and will ignore the first data column. 
If the input FITS file contains several
extensions or HDUs, the one to be read can be specified thanks to the CFITSIO 
\htmladdnormallink{Extended File Name Syntax}{https://heasarc.gsfc.nasa.gov/docs/software/fitsio/c/c_user/node81.html}, using its number (eg, {\tt file.fits[2]} or {\tt file.fits+2}) or its
{\tt EXTNAME} value (eg. {\tt file.fits[beam\_100x100]}). By default, only the first valid
extension will be read.}
{\modFitstools}
\end{facility}

\begin{f90format}
{\mylink{sub:fits2cl:filename}{filename}%
, \mylink{sub:fits2cl:clin}{clin}%
, \mylink{sub:fits2cl:lmax}{lmax}%
, \mylink{sub:fits2cl:ncl}{ncl}%
, \mylink{sub:fits2cl:header}{header}%
, [\mylink{sub:fits2cl:units}{units}%
]}
\end{f90format}

\begin{arguments}
{
\begin{tabular}{p{0.4\hsize} p{0.05\hsize} p{0.1\hsize} p{0.35\hsize}} \hline  
\textbf{name~\&~dimensionality} & \textbf{kind} & \textbf{in/out} & \textbf{description} \\ \hline
                   &   &   &                           \\ %%% for presentation
filename\mytarget{sub:fits2cl:filename}(LEN=\filenamelen) & CHR & IN & the FITS file containing the power spectrum. \\
lmax\mytarget{sub:fits2cl:lmax} & I4B & IN & Maximum $\ell$ value to be read. \\
ncl\mytarget{sub:fits2cl:ncl} & I4B & IN & 1 for temperature coeffecients only, 4 for polarisation. \\
clin\mytarget{sub:fits2cl:clin}(0:lmax,1:ncl) & SP/ DP & OUT & the power spectrum read from the file.\\
header\mytarget{sub:fits2cl:header}(LEN=80) (1:) & CHR & OUT & the header read from the FITS-file. \\ 
units\mytarget{sub:fits2cl:units}(LEN=80) (1:) & CHR & OUT & the column units read from the FITS-file. \\ 
\end{tabular}
}
\end{arguments}

%\newpage
\begin{example}
{
use \htmlref{healpix\_modules}{sub:healpix_modules}\\
%implicit none \\
real(\mylink{sub:healpix_types:sp}{SP}), allocatable, dimension(:,:) :: cl \\
character(len=80), dimension(1:300) :: header \\
character(len=80), dimension(1:100) :: units \\
integer(\mylink{sub:healpix_types:i4b}{I4B}) :: lmax, ncl, np \\
character(len=\mylink{sub:healpix_types:filenamelen}{filenamelen}) :: fitsfile='cl.fits' \\
%fitsfile = 'cl.fits' \\
np = \htmlref{getsize\_fits}{sub:getsize_fits}(fitsfile, nmaps=ncl, mlpol=lmax) \\
allocate(cl(0:lmax, 1:ncl)) \\
call fits2cl(fitsfile, cl, lmax, ncl, header, units)  \\
%call fits2cl(fitsfile,cl,64,4,header,units)  \\
}
{
Reads a power spectrum from the FITS file {\tt `cl.fits'} and stores the result in 
{\tt \mylink{sub:fits2cl:clin}{cl}(0:lmax,1:ncl)} 
which are the \mylink{sub:fits2cl:ncl}{\tt ncl} $C_\ell$ coefficients up to 
$\ell=$\mylink{sub:fits2cl:lmax}{\tt lmax}. 
The FITS header is returned in \mylink{sub:fits2cl:header}{\tt header}, 
the column units in \mylink{sub:fits2cl:units}{\tt units}.
% Reads a power spectrum from the FITS file `cl.fits' and stores the result in cl(0:64,1:4) which are the $C_l$ coeffecients up to $l=64$ for ($T$, $E$, $B$, $T\times E$). The FITS header is returned in header, the column units in units.
}
\end{example}
\begin{modules}
  \begin{sulist}{} %%%% NOTE the ``extra'' brace here %%%%
  \item[\textbf{fitstools}] module, containing:
  \item[printerror] routine for printing FITS error messages.
  \item[\textbf{cfitsio}] library for FITS file handling.		
  \end{sulist}
\end{modules}

\begin{related}
  \begin{sulist}{} %%%% NOTE the ``extra'' brace here %%%%
  \item[\htmlref{create\_alm}{sub:create_alm}] Routine to create $a_{\ell m}$ values
  from an input power spectrum.
  \item[\htmlref{write\_asctab}{sub:write_asctab}] Routine to create an ascii
  FITS file containing a power spectrum.
  \item[\htmlref{getsize\_fits}{sub:getsize_fits}] Routine to parse FITS file header, and determine the data storage features.
% and, for instance, determine \mylink{sub:fits2cl:lmax}{lmax} and \mylink{sub:fits2cl:ncl}{ncl}
  \item[\htmlref{getnumext\_fits}{sub:getnumext_fits}] Routine to determine number of extensions of a FITS file.
  \end{sulist}
\end{related}

\rule{\hsize}{2mm}

\newpage
