
\sloppy


\title{\healpix Fortran Facility User Guidelines}
\docid{map2gif} \section[map2gif]{\nosectionname}
\label{fac:map2gif}
\docrv{Draft 0.7}
\author{Anthony J.~Banday}
\abstract{This document describes the \healpix facility map2gif.}

\begin{facility}
{This Fortran facility provides a means to generate a
gif image from an input \healpix sky map. It is intended to allow some
primitive visualisation for those with limited or no access to IDL. 
It is also useful for image generation in a pipeline environment.}
{src/f90/map2gif/map2gif.f90}
\end{facility}

\begin{f90facility}
{map2gif}
\end{f90facility}

\begin{qualifiers}
  \begin{qulist}{} %%%% NOTE the ``extra'' brace here %%%%
    \item[{- bar}] Logical which determines whether a color bar is
      displayed \default{.false.}. 
    \item[{- col}] The number of the color table to utilise \default{5}.
    \item[{- hlp}] Print on-line help for the facility.
    \item[{- inp}] The file name of the input FITS sky map \nodefault.
    \item[{- log}] Logical to use the log of the signal when plotting 
      \default{.false.}
    \item[{- ash}] Logical to use the hyperbolic arc sine of the signal when
      plotting. Cannot be true when -log is true.
      \default{.false.}
    \item[{- add}] Real value to add to the signal before performing any
      other operation to it (like taking the logarithm etc.)
      \default{0.0}
    \item[{- mul}] Real value to multiply the signal with directly after
      adding the offset (see above).
      \default{1.0}
    \item[{- min}] Set the minimum value for the plotted signal
    \default{is to use the actual signal minimum}.
    \item[{- max}] Set the maximum value for the plotted signal
      \default{is to use the actual signal maximum}.
    \item[{- pro}] Select the projection scheme \default{Mollweide}.
    \item[{- out}] The file name of the output gif image \nodefault.
    \item[{- sig}] The identifier of the signal to plot: for a
      polarisation map, then the mapping is 1 = I; 2 = Q; 3 = U
      \default{1}.
    \item[{- ttl}] A string specifying the title for the plot \nodefault.
    \item[{- xsz}] The x-dimension of the image in pixels \default{800}.
  \end{qulist}
\end{qualifiers}

\begin{codedescription}
{map2gif reads in a \healpix sky map in FITS format and generates an
image in GIF format. map2gif allows the selection of the projection
scheme (Mollweide or Gnomonic for small patches of the sky), color
table, color bar inclusion, linear or log scaling, maximum and 
minimum range for the plot and plot-title. The facility utilises
a command-line interface.}
\end{codedescription}

\begin{datasets}
{
\begin{tabular}{p{0.3\hsize} p{0.35\hsize}} \hline  
  \textbf{Dataset} & \textbf{Description} \\ \hline
                   &                      \\ %%% for presentation
  None required & \\ 
                   &                      \\ \hline %%% for presentation
\end{tabular}
} 
\end{datasets}

\begin{support}
  \begin{sulist}{} %%%% NOTE the ``extra'' brace here %%%%
  \item[xv] xv or a similar facility is required to view the
            gif image generated by map2gif (a browser can also 
            be used).
  \item[\htmlref{synfast}{fac:synfast}] This \healpix facility will generate the FITS format 
            sky map to be input to map2gif.
  \end{sulist}
\end{support}


\begin{examples}{1}
{
\begin{tabular}{ll} %%%% use this tabular format %%%%
map2gif & -inp planck100GHZ-LFI.fits \\
        & -out planck100GHZ-LFI.gif \\
        & -bar .true. \\
        & -min -100 \\
        & -max 100 \\
        & -ttl Simulated Planck LFI Sky Map at 100GHz \\
\end{tabular}
}
{map2gif reads in the map `planck100GHZ-LFI.fits' and generates
an output gif image with name `planck100GHZ-LFI.gif' in which
the temperature scale has been set to lie between $\pm$ 100 ($\mu$K), 
a color bar has been drawn and the title `Simulated Planck
LFI Sky Map at 100GHz' appended to the image.
}
\end{examples}

\begin{release}
  \begin{relist}
    \item Initial release (\healpix 1.00)
%    \item Updated with new rotation and projection facilities (\healpix
%    1.01) %%%% This is what we would invisage for additional releases %%%%
  \end{relist}
\end{release}

\begin{messages}
{
\begin{tabular}{p{0.25\hsize} p{0.1\hsize} p{0.35\hsize}} \hline  
  \textbf{Message} & \textbf{Severity} & \textbf{Text} \\ \hline
                   &                   &   \\ %%% for presentation
   None at present &                   &   \\ 
                   &                   &   \\ \hline %%% for presentation
\end{tabular}
} 
\end{messages}

\rule{\hsize}{2mm}

\newpage
