
\sloppy

% corrected example, 2007-Jan
\title{\healpix Fortran Subroutines Overview}
\docid{output\_map*} \section[output\_map*]{ }
\label{sub:output_map}
\docrv{Version 1.3}
\author{Eric Hivon}
\abstract{This document describes the \healpix Fortran90 subroutine OUTPUT\_MAP.}

\begin{facility}
{This routine writes a full sky \healpix map into a FITS file. The map can be
  either single or double precision real. It {\em has} to be 2-dimensional.}
{\modFitstools}
\end{facility}

\begin{f90format}
{map, header, filename \optional{[,extno]}}
\end{f90format}

\begin{arguments}
{
\begin{tabular}{p{0.3\hsize} p{0.05\hsize} p{0.08\hsize} p{0.5\hsize}} \hline  
\textbf{name~\&~dimensionality} & \textbf{kind} & \textbf{in/out} & \textbf{description} \\ \hline
                   &   &   &                           \\ %%% for presentation
map(0:,1:) 		& SP/ DP 	& IN & full sky map(s) to be output \\
header(LEN=80)(1:) 	& CHR 	& IN & string array containing the
                   FITS header to be included in the file \\
filename(LEN=*) & CHR & IN & filename of the FITS-file to
                   contain \healpix map(s). \\
\optional{extno} \hskip 4cm & I4B & IN & extension number in which to write the data (0
                   based). \default 0
\end{tabular}
}
\end{arguments}

\begin{example}
{
use healpix\_types \\
use fits\_tools, only : output\_map \\
real(sp), dimension(0:12*16**2-1, 1:1) :: map \\
character(len=80), dimension(1:10) :: header \\
header(:) = '' \\
map(:,:) = 1. \\
call output\_map(map, header, 'map.fits')
}
{generates a simple map (made of 1s) and outputs it into the FITS file {\tt map.fits}
}
\end{example}
\newpage
\begin{modules}
  \begin{sulist}{} %%%% NOTE the ``extra'' brace here %%%%
  \item[\textbf{fitstools}] module, containing:
  \item[printerror] routine for printing FITS error messages.
  \item[write\_bintab] routine to write a binary table into a FITS file.
  \item[\textbf{cfitsio}] library for FITS file handling.		
  \end{sulist}
\end{modules}

\begin{related}
  \begin{sulist}{} %%%% NOTE the ``extra'' brace here %%%%
  \item[anafast] executable that reads a \healpix map from a FITS file
  and analyses it. 
  \item[synfast] executable that generate full sky \healpix maps
  \item[\htmlref{input\_map}{sub:input_map}] subroutine to read a \healpix map from a a FITS file
  \item[\htmlref{write\_bintabh}{sub:write_bintabh}] subroutine to write a large
  array into a FITS file piece by piece
  \item[\htmlref{input\_tod*}{sub:input_tod}] subroutine to read an arbitrary subsection of
  a large binary table
  \item[\htmlref{write\_minimal\_header}{sub:write_minimal_header}] routine to
write minimal FITS header
  \end{sulist}
\end{related}

\rule{\hsize}{2mm}

\newpage
