
\sloppy


\title{\healpix Fortran Subroutines Overview}
\docid{read\_dbintab} \section[read\_dbintab]{ }
\label{sub:read_dbintab}
\docrv{Version 1.1}
\author{Frode K.~Hansen}
\abstract{This document describes the \healpix Fortran90 subroutine READ\_DBINTAB.}

\begin{facility}
{This routine reads a double precision binary array from a FITS-file. It is used by \healpix to read precomputed $P_{lm}(\theta)$ values and pixel window functions.}
{src/f90/mod/fitstools.F90}
\end{facility}

\begin{f90format}
{filename, map, npixtot, nmaps, nullval, anynull, units}
\end{f90format}

\begin{arguments}
{
\begin{tabular}{p{0.4\hsize} p{0.05\hsize} p{0.1\hsize} p{0.35\hsize}} \hline  
\textbf{name~\&~dimensionality} & \textbf{kind} & \textbf{in/out} & \textbf{description} \\ \hline
                   &   &   &                           \\ %%% for presentation
filename(LEN=\filenamelen) & CHR & IN & filename of FITS-file containing the double precision array. \\
npixtot & I4B & IN & Number of values to be read from the file.\\
nmaps & I4B & IN & number of 1-dim. arrays, 1 for scalar $P_{lm}\!\!$ s and pixel windows, 3 for scalar and tensor $P_{lm}\!\!$ s. \\
map(0:npixtot-1,1:nmaps) & DP & OUT & the array read from the FITS-file.\\
nullval & DP & OUT & value of missing pixels in the array. \\
anynull & LGT & OUT & TRUE, if there are missing pixels, and FALSE otherwise. \\
units(len=20)(1:nmaps) & CHR & OUT & respective physical units of the maps in the FITS file.
\end{tabular}
}
\end{arguments}
\newpage

\begin{example}
{
call read\_dbintab ('plm\_32.fits',plm,65*66*32,1,nullval,anynull)  \\
}
{
Reads precomputed scalar $P_{lm}(\theta)$ from the file `plm\_32.fits'. The values are returned in the array plm(0:65*66*32,1:1). The number of values 65*66*32 is the number of precomputed $P_{lm}(\theta)$ for a $N_{side}=32$, $lmax=64$ map. If there are missing values in the file, anynull is TRUE and nullval contains the values of these pixels.
}
\end{example}

\begin{modules}
  \begin{sulist}{} %%%% NOTE the ``extra'' brace here %%%%
  \item[\textbf{fitstools}] module, containing:
  \item[printerror] routine for printing FITS error messages.
  \item[\textbf{cfitsio}] library for FITS file handling.		
  \end{sulist}
\end{modules}

\begin{related}
  \begin{sulist}{} %%%% NOTE the ``extra'' brace here %%%%
  \item[plmgen] Executable to create files with precomputed $P_{lm}(\theta)$.
  \item[\htmlref{write\_plm}{sub:write_plm}] Routine to create a file to be read by read\_dbintab.
  \end{sulist}
\end{related}

\rule{\hsize}{2mm}

\newpage
