
\sloppy


\title{\healpix Fortran Subroutines Overview}
\docid{write\_bintabh} \section[write\_bintabh]{ }
\label{sub:write_bintabh}
\docrv{Version 1.1}
\author{Frode K.~Hansen}
\abstract{This document describes the \healpix Fortran90 subroutine WRITE\_BINTABH.}

\begin{facility}
{This routine is designed to write large (or huge) arrays into a binary table
extension of a FITS file. The user can
choose to write the array piece by piece. This is designed to deal with Time
Ordered Data set (tod).}
{src/f90/mod/fitstools.f90}
\end{facility}

\begin{f90format}
{tod, npix, ntod, header, nlheader, filename, \optional{[extno, firstpix, repeat]}}
\end{f90format}
\aboutoptional

\begin{arguments}
{
\begin{tabular}{p{0.35\hsize} p{0.05\hsize} p{0.08\hsize} p{0.45\hsize}} \hline  
\textbf{name~\&~dimensionality} & \textbf{kind} & \textbf{in/out} & \textbf{description} \\ \hline
                   &   &   &                           \\ %%% for presentation
tod(0:npix-1,1:ntod) & SP & IN & the map or tod
  to write to the FITS-file. It will be written in the file at the location
                   corresponding to pixels (or time samples)
                   {\tt firstpix} to {\tt firtpix + npix} -1.\\
npix & I8B & IN & Number of pixels or time samples in the map or TOD. See Note below.\\
ntod & I4B & IN & number of maps or tods to be written. \\
header(LEN=80) (1:nlheader) & CHR & IN & The header for the FITS-file. \\
nlheader & I4B & IN & number of header lines to write to the file. \\
filename(LEN=\filenamelen) & CHR & IN & the array is written into a FITS-file with this filename. \\
\optional{extno} & I4B & IN & extension number in which to write the data (0
                   based).  \default 0 \\
\optional{firstpix} & I8B & IN & 0 location in the FITS file of the first
                   pixel (or time sample) to be written (0 based). \default 
                   0. See Note below.
                   \\
\optional{repeat} & I4B & IN & length of the element vector used in the binary
                   table. \default{1024} if {\tt npix} $\propto 1024$; 12000 if
                   {\tt npix} $> 12000$ and 1 otherwise. Choosing a large {\tt
                   repeat} for multi-column tables ({\tt ntod} $>1$) generally
                   speeds up the I/O. It also helps bringing the number of rows
                   of the table under $2^{31}$, which is a hard limit of
                   cfitsio. 
\end{tabular}
{\bf Note :} Indices and number of data elements larger than
                   $2^{31}$ are only accessible in FITS files on computers with 64 bit
                   enabled compilers and with some specific compilation options of
                   cfitsio (see cfitsio documentation).
}
\end{arguments}

\begin{example}
{
use healpix\_types \\
use fitstools, only : \thedocid \\
character(len=80), dimension(1:128) :: hdr \\
real(SP), dimension(0:49,1) :: tod \\
hdr(:) = ' ' \\
tod(:,1) = 1. \\
call \thedocid (tod, 50\_i8b, 1, header, 128, 'tod.fits', firstpix=0\_i8b, repeat=10)  \\
tod = tod * 3. \\
call \thedocid (tod, 20\_i8b, 1, header, 128, 'tod.fits', firstpix=40\_i8b)  
}
{
Writes into the FITS file `tod.fits' a 1 column binary table, where the first 40
data samples have the value $1.$ and the next 20 have the value $3.$ (Note that
in this example the
second call to \thedocid \ overwrites some of the pixels written by the first call). The samples will be
written in element vectors of length 10. The header for the FITS-file is given in the
string array {\tt hdr} and the number of lines in the header is 128. 
}
\end{example}

\begin{modules}
  \begin{sulist}{} %%%% NOTE the ``extra'' brace here %%%%
  \item[\textbf{fitstools}] module, containing:
  \item[printerror] routine for printing FITS error messages.
  \item[\textbf{cfitsio}] library for FITS file handling.		
  \end{sulist}
\end{modules}

\begin{related}
  \begin{sulist}{} %%%% NOTE the ``extra'' brace here %%%%
  \item[\htmlref{input\_tod*}{sub:input_tod}] routine that reads a file created by \thedocid. 
  \item[\htmlref{input\_map}{sub:input_map},
  \htmlref{read\_bintab}{sub:read_bintab}] routines to read \healpix sky map,
  \item[\htmlref{write\_minimal\_header}{sub:write_minimal_header}] routine to write minimal FITS header
  \end{sulist}
\end{related}

\rule{\hsize}{2mm}

\newpage
